\documentclass[10pt]{article}
\begin{document}
\noindent\parbox{7cm}{\large Purdue University\\
                    MA265 Linear Algebra\\
                    Fall 2014\\
                    Syllabus}
\hfill
\parbox{7cm}{\large Instructor: Edinah Gnang\\
                    Office: 646 MATH\\
                    E-mail: {\tt egnang@purdue.edu}}

\section{General Information}

\subsection{Class time / location:}
        Monday, Wednesday, Friday 03:30p - 04:20p, UNIV 303.

\subsection{Office Hours:}   
                Monday 1:00p - 3:00p.	

\subsection{Textbook:}
                Elementary Linear Algebra\\
                B. Kolman, D. Hill\\
		9th Edition, Prentice Hall 2007.\\
\\
                Lab Manual: Linear Algebra with Matlab\\
		D. Hill, D. Zitarelli\\
		3rd edition, Prentice Hall 2004.\\
\\
                Matlab files and Supplementary exercises: see
                department course web page {\tt http://www.math.purdue.edu/academic/courses/MA26500/}.
\subsection{Webpages:}
\noindent The department course webpage is {\tt http://www.math.purdue.edu/ma26500}. \smallskip
This page contains matlab files to
download for you. These will be needed during the course for
homework.\smallskip

\noindent Our class page is {\tt https://github.com/gnang/MA26500}. It includes syllabus,
and some other info concerning the class. \smallskip

\noindent The WebAssign student login page is {\tt http://www.webassign.net/purdue/login.html}.

\subsection{Statement for Students with Disabilities}
See the webpage, {\tt http://www.math.purdue.edu/\~{}walther/teach}.

\subsection{Calculators}
Calculators are not allowed on any test.

\newpage 
~
\vspace{-3cm}
\section{Course Structure}

If you disagree with the grading in any category, you need to resubmit
the item in question {\bf with a written explanation} stating {\em why} (and
not just {\em that}) you deserve more credit. 
\subsection{Homework:}   
        Webassign is due online Thursday evening 11:40pm.  The
        other problems (with a * on the assignment sheet, including
        all Matlab problems), will be collected every Friday in
        class. {\bf No late assignments will be accepted.}  
        Neither will homework deposited anywhere else.

	The homework due in any given week is the
	homework corresponding to the material of the previous
	week. Homework must be readable and {\bf must be stapled}. Illegible
	scribblings will receive no credit from the grader.

        You are encouraged to attempt all the questions and discuss
        with your classmates. However, the write-up must
        be of your own.

\subsection{Quizzes}
There will likely be weekly quizzes.

\subsection{Midterms:}  
	There will be two midterms, {\bf Friday, Oct 3} and {\bf
  Friday, Nov 7}. Makeups may be given in extraordinary
  instances, but only with documented reasons.

\subsection{Final Exam:}
        The Final Exam will be given during the Final Exam Week.
        The location and date of the final will be announced in class.
	All exams will be multiple choice.

\subsection{Course Grade:}
        Your course grade will be determined using the following 
        distributions:

\begin{tabular}{ll}\\
        HW 		 &    25\%\\
        2 Midterms, each     &  20\%\\
        Final           &     35\%\\
\end{tabular}

\subsection{Classroom Safety}
In the event of a major campus emergency, course requirements,
deadlines and grading percentages are subject to changes that may be
necessitated by a revised semester calendar or other circumstances
beyond the instructor's control. Here are ways to get information
about changes in this course.

\begin{itemize}
\item Course and class web pages (see item 1.4)
\item \tt{egnang@purdue.edu}.
\end{itemize}
\end{document}

