\documentclass[10pt]{article}
\begin{document}
\noindent\parbox{7cm}{\large Purdue University\\
                    MA26500 Linear Algebra\\
                    Fall 2016\\
                    Syllabus}
\hfill
\parbox{7cm}{\large Instructor: Edinah Gnang\\
                    Office: 404 MATH\\
                    Phone:   (765) 494-1901\\
                    E-mail: {\tt egnang@math.purdue.edu}}

\section{General Information}

\subsection{Class time / location:}
                    MWF 09:30am-10:20am, UNIV 303 (Sec 071)\\
                    MWF 10:30am-11:20am, UNIV 303 (Sec 011)\\ 

\subsection{Office Hours:}   
		    MWF 11:20-12:40

\subsection{Textbook:}
                Elementary Linear Algebra\\
                B. Kolman, D. Hill\\
		9th Edition, Prentice Hall 2007.\\
\\
                Lab Manual: Linear Algebra with Matlab\\
		D. Hill, D. Zitarelli\\
		3rd edition, Prentice Hall 2004.\\
\\
                Matlab files and Supplementary exercises: see
                department course web page {\tt http://www.math.purdue.edu/academic/courses/MA26500/}.
\subsection{Webpages:}
\noindent The department course webpage is {\tt http://www.math.purdue.edu/ma26500}. \smallskip
This page contains matlab files to
download for you. These will be needed during the course for
homework.\smallskip

\noindent Our class page can be found on the page {\tt
http://www.math.purdue.edu/\~{}egnang/}. It includes
syllabus, some other info concerning the class. \smallskip


\noindent The WebAssign student login page is {\tt http://www.webassign.net/purdue/login.html}.


%\subsection{Statement for Students with Disabilities}
%See the webpage, {\tt http://www.math.purdue.edu/\~{}walther/teach}.

\subsection{Calculators}
Calculators are not allowed on any test.


\newpage 
~
\vspace{-3cm}
\section{Course Structure}

If you disagree with the grading in any category, you need to resubmit
the item in question {\bf with a written explanation} stating {\em why}
(and not just {\em that}) you deserve more credit. 
\subsection{Homework:}   
        Webassign is due online Thursday evening 11:40pm.  The
        other problems (with a * on the assignment sheet, including
        all Matlab printout), will be collected every Friday in
        class or in my office during the Friday office hours.  
        {\bf No late assignments will be accepted.}  Neither will 
        homework deposited anywhere else.

	The homework due in any given week is the
	homework corresponding to the material of the previous
	week. Homework must be readable and {\bf must be stapled}. Illegible
	scribblings will receive no credit from the grader.

        You are encouraged to attempt all the questions and discuss
        with your classmates. However, the write-up must
        be of your own.

\subsection{Quizzes}
There will likely be weekly quizzes.

\subsection{Midterms:}  
	There will be two midterms, {\bf Friday Sep. 30th} and 
  {\bf Friday Nov. 4th}. Makeups may be given in extraordinary
  instances, but only with documented reasons.

\subsection{Final Exam:}
        The Final Exam will be given during the Final Exam Week.
        The location and date of the final will be announced in class.
	All exams will be multiple choice.

\subsection{Course Grade:}
        Your course grade will be determined using the following 
        distributions:

\begin{tabular}{ll}\\
        HW 		&    25\%\\
        2 Midterms, each     &  20\%\\
        Final          &     35\%\\
\end{tabular}


\subsection{Classroom Safety}
In the event of a major campus emergency, course requirements,
deadlines and grading percentages are subject to changes that may be
necessitated by a revised semester calendar or other circumstances
beyond the instructor's control. Here are ways to get information
about changes in this course.

\newpage 

\section{DRC}
 
 If you have been certified by the Disability Resource Center (DRC) as
 eligible for academic adjustments on exams or quizzes see
 www.math.purdue.edu/ada for exam and quiz procedures for your mathematics
course or go to MATH 202 for paper copies.
In the event that you are waiting to be certified by the Disability Resource
Center we encourage you to review our procedures prior to being certified.
For all in-class accommodations please see your instructor outside class
hours ­ before or after class or during office hours ­ to share your
Accommodation Memorandum for the current semester and discuss your
accommodations as soon as possible.


\begin{itemize}
\item Course and class web pages (see item 1.4)
\item \tt{egnang@purdue.edu}, \tt{(765) 494-1901}.
\end{itemize}
\end{document}
